BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-12-28 Paper2/BOAST.tex
section related work
section ack

%%% NON REGRESSION TESTING USING TRACE DEBUGGING %%%
\subsection{Non Regression Testing Using Trace Debugging\abel{sec:gputrace}}

@@

The research leading to these results has received funding from the European
Community's Seventh Framework Programme [FP7/2007-2013] under grant agreement
\Num 288777 and 610402.

>>>>

%%% NON REGRESSION TESTING USING TRACE DEBUGGING %%%
\subsection{Non Regression Testing Using Trace Debugging\label{sec:gputrace}}

@@

The research leading to these results has received funding from the European
Community's Seventh Framework Programme [FP7/2007-2013] under grant agreements
\Num 288777 and 610402.
